Normalized Coherence

### 2019-09-17 Analysis/Normalized_Coherence.Rmd
??? BUG?

  # Create empty list
  mod_over = list()
  # Set index for list entries
  index = 1
  # Loop through each pathway
  for (j in unique(msig$gs_name)) {
    #Subset to only include current pathway
    curr_msig = msig %>% filter(gs_name == j)
    #Write to table in format for disease2frame
    write.table(curr_msig$gene_symbol, file = "temp_rea_bio.txt", quote = FALSE, row.names = FALSE, col.names = FALSE)
    #Get internal/external connectivity
    diseases_curr = diseases2frame("temp_rea_bio.txt", links = biogrid)
    #Get disease name
    diseases_curr = diseases_curr %>% mutate(Disease = j)
    mod_over[[index]] = diseases_curr
    index =  index+1
  }

>>>>

  # Create empty list
  mod_over = list()
  # Set index for list entries
  index = 1
  # Loop through each pathway
  for (j in unique(msig$gs_name)) {
    #Subset to only include current pathway
    curr_msig = msig %>% filter(gs_name == j)
    #Write to table in format for disease2frame
    write.table(curr_msig$gene_symbol, file = "temp_rea_bio.txt", quote = FALSE, row.names = FALSE, col.names = FALSE)
    #Get internal/external connectivity
    diseases_curr = diseases2frame("temp_rea_bio.txt", links = biogrid) # [??? Shouldn't it be database?]
    #Get disease name
    diseases_curr = diseases_curr %>% mutate(Disease = j)
    mod_over[[index]] = diseases_curr
    index =  index+1
  }
